---
title: "RSV Cost-effectiveness model for BC"
subtitle: "Includes individual characteristics"
author: "Javad Taleshi ã Optimized Version"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(scipen = 999)  # disable scientific notation
rm(list = ls())
gc()
```



# Load packages

```{r }
if (!require('pacman')) install.packages('pacman'); library(pacman) 
# load (install if required) packages from CRAN
p_load("devtools", "dplyr", "scales", "ellipse", "ggplot2", "lazyeval",
       "igraph", "truncnorm", "ggraph", "reshape2", "knitr", "markdown", 
       "stringr", "dampack", "matrixStats")
# load (install if required) packages from GitHub
#install_github("DARTH-git/darthtools", force = TRUE) # Uncomment if there is a newer version
p_load_gh("DARTH-git/darthtools")
```


## Model input

## General setup 
```{r}

# Time and population parameters
cycle_length   <- 1/12       # one month
n_cycles       <- 24         # time horizon in cycles
n_i            <- 100000      # number of births per year ########################################################


v_names_cycles <- paste("cycle", 0:n_cycles)
v_names_states <- c("NB", "H", "RSV", "D")
n_states       <- length(v_names_states)

# Treatment categories
v_names_treatments <- c("NT", "DV", "ED", "ICU", "PW")
n_treatments       <- length(v_names_treatments)

# Discounting factors
d_c <- 0.000   # cost discount rate
d_e <- 0.000   # QALY discount rate


# We investigate these vaccine strategies:
#"No Intervention"
#"Palivizumab"
#"Nirsevimab (High)"
#"Nirsevimab (High & Mod)"
#"RSVpreF + Nirsevimab (High)"
#"RSVpreF + Nirsevimab (High & Mod)"
#"Nirsevimab (Universal)"

# Strategies
v_names_str <- c("No Intervention",
                 "Palivizumab",
                 "Nirsevimab (High & Mod)",
                 "RSVpreF",
                 "RSVpreF + Nirsevimab (High)",
                 "RSVpreF + Nirsevimab (High & Mod)",
                 "Nirsevimab (Universal)")
n_str <- length(v_names_str)

# Vaccine coverage and efficacies (as in your original code)
#coverage_palivizumab_y1 <- 1 
#coverage_RSVpreF        <- 0.65
#coverage_nirsevimab_ModerateRisk     <- 0.7
coverage_nirsevimab_HighRisk     <- 1


  #vaccine efficacy
  
  # Efficacy for palivizumab from NACI
  eff_RSVMA_palivizumab  <- 0.70
  eff_inpat_palivizumab  <- 0.82
  eff_ICU_palivizumab    <- 0.82
  
  
  # Efficacy for RSVpreF from Kampmann 2023
  valid_months_RSVpreF <- 5
  efficacy_RSVMA_RSVpreF  <- 0.525
  efficacy_inpat_RSVpreF  <- 0.564
  efficacy_ICU_RSVpreF    <- 0.709

  # Efficacy for nirsevimab from Simûçes 2023
  valid_months_nirsevimab <- 5
  efficacy_RSVMA_nirsevimab  <- 0.795
  efficacy_inpat_nirsevimab  <- 0.773
  efficacy_ICU_nirsevimab    <- 0.860
  
  # Efficacy for nirsevimab from NACI
  #valid_months_nirsevimab <- 5
  #efficacy_RSVMA_nirsevimab  <- 0.80
  #efficacy_inpat_nirsevimab  <- 0.81
  #efficacy_ICU_nirsevimab    <- 0.90



# The month that the efficacy of vaccines go to zero
zero_month <- 10

# Define the RSV season
sim_start_month         <- 5  
rsv_season_start_month  <- 11
sim_to_rsv_month_gap <- rsv_season_start_month - sim_start_month


# Probabilities to calculate outpatient treatments
prob_RSVMA_Inp          <- c(rep(0.083, 6), rep(0.021, 6), rep(0.027, n_cycles - 12))
prob_Outp_ED            <- c(rep(0.29, 6), rep(0.24, 6), rep(0.33, n_cycles - 12))

# Costs and disutilities (as in your original code)
c_NT  <- 0

u_H <- 1
u_Total <- 45.3              # Discounted total years to live for a human
u_rs <- u_Total - (n_cycles-6) * cycle_length  # Mean Utility for rest of the life, on average the age of infants would be n_cycles-6 at the end of simulation


#############################################################################################
#############################################################################################
l_params <- list(
  
  base_str = "No Intervention", # Base strategy
  
  n_sim = 10,        # Number of simulations for each strategy #######################################################

  PD_ICU = 4615, # Cost per day for ICU, from Vadlamudi 2025
  PD_PW = 2283,  # Cost per day for PW, from Vadlamudi 2025

  c_ED  = 342,            # Cost of ED visit, from Shoukat 2023
  c_DV = 229,            # Cost of doctor visit, from Shoukat 2023

  c_RSVpreF           = 125,        # Price of RSVpreF per dose
  c_nirsevimab         = 450,      # Price of nirsevimab per dose
  c_Admin_vac         = 15,        # cost of admin per dose of vaccine
  
  c_palivizumab       = 3600,  # cost of pvz per season
  c_Admin_palivizumab = 150,       # Cost of admin for pvz
  
  # Disutility for each treatment
  Du_ICU_Infants = 0.0245,
  Du_ICU_Caregivers = 0.0097,
  
  Du_PW_Infants  = 0.0169,
  Du_PW_Caregivers  = 0.0067,
  
  Du_ED_Infants  = 0.0135, 
  Du_ED_Caregivers  = 0.00675,
  
  Du_DV_Infants  = 0.00845,
  Du_DV_Caregivers  = 0.00423,
  
  
  # vaccine coverage
  coverage_RSVpreF  = 0.65,
  coverage_nirsevimab_ModerateRisk  = 0.7,
  
  #vaccine efficacy
  # pvz
  eff_RSVMA_palivizumab  = eff_RSVMA_palivizumab,
  
  # Efficacy for RSVpreF from Kampmann 2023
  efficacy_RSVMA_RSVpreF  = efficacy_RSVMA_RSVpreF,

  # Efficacy for RSVpreF from Simûçes 2023
  efficacy_RSVMA_nirsevimab  = efficacy_RSVMA_nirsevimab
  
)

v_dwc <- 1 / ((1 + (d_e * cycle_length)) ^ (0:n_cycles))
v_dwe <- 1 / ((1 + (d_c * cycle_length)) ^ (0:n_cycles))


```


## Get the inputs from the file

```{r}
##################################################################################
##################################################################################
# Set the path to the CSV file
file_path <- "./Data/RSV_AllMetrics_withCI.csv"

# Read the CSV file
AllMetrics_list <- read.csv(file_path)


# Extract the relevant probabilities
prob_LowRisk  <- AllMetrics_list[AllMetrics_list$Variable == "prob_LowRisk", "Mean"]
prob_highrisk    <- AllMetrics_list[AllMetrics_list$Variable == "prob_HighRisk", "Mean"]

# Calculate the risk probabilities with updated HighRisk and LowRisk definitions
v_risk_prob <- c(
  HighRisk   = prob_highrisk,
  LowRisk    = prob_LowRisk,
  ModerateRisk = 1-prob_highrisk-prob_LowRisk
  
)

# pvz coverage in the second season 
coverage_palivizumab_y2 <- AllMetrics_list[AllMetrics_list$Variable == "pvz_coverage_second_season", "Mean"]


# Monthly mortality rate
l_params$p_mort <- AllMetrics_list[AllMetrics_list$Variable == "monthly_mortality", "Mean"]
l_params$p_mort_Inp <- l_params$p_mort

# Probability of ICU admission, condition on hospitalization
l_params$Prob_ICU_LowRisk <- AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_LowRisk", "Mean"]
l_params$Prob_ICU_ModerateRisk <- AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_ModerateRisk", "Mean"]
l_params$Prob_ICU_HighRisk <- AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_HighRisk", "Mean"]

RR_Prob_ICU_Second_season <- AllMetrics_list[AllMetrics_list$Variable == "RR_Prob_ICU_Second", "Mean"]

# Length of stay for hospitalization, without ICU 
l_params$LOS_hosp_LowRisk <- AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_LowRisk", "Mean"]
l_params$LOS_hosp_ModerateRisk <- AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_ModerateRisk", "Mean"]
l_params$LOS_hosp_HighRisk <- AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_HighRisk", "Mean"]


# Length of stay in ICU
l_params$LOS_icu_LowRisk <- AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_LowRisk", "Mean"]
l_params$LOS_icu_ModerateRisk <- AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_ModerateRisk", "Mean"]
l_params$LOS_icu_HighRisk <- AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_HighRisk", "Mean"]

########################################################################################
########################################################################################
# Read the coefficients for probability of hospitalization from the file

# Read in the coefficients for hospitalization
Hosp_model_coef <- read.csv("./Data/RSV_Hosp_model_coefficients.csv", stringsAsFactors = FALSE)
Hosp_model_beta <- setNames(Hosp_model_coef$estimate, Hosp_model_coef$term)

```


# Define a function for calculating vaccine efficiancy  
```{r}
#############################################################################
#############################################################################
vaccine_efficacy <- function(efficacy, valid_months, zero_month = zero_month) {
  # Create a vector of zeros for all cycles
  eff_vec <- numeric(n_cycles)
  
  # Set constant efficacy for the first valid_months
  if (n_cycles >= valid_months) {
    eff_vec[1:valid_months] <- efficacy
  } else {
    eff_vec[1:n_cycles] <- efficacy
    return(eff_vec)
  }
  
  # Calculate efficacy for months between valid_months and zero_month
  if (n_cycles > valid_months) {
    # Determine the last month in the decline period (up to n_cycles if n_cycles < zero_month)
    decline_end <- min(zero_month, n_cycles)
    # Create a sequence for the months in the decline period
    decline_months <- (valid_months + 1):decline_end
    # For each month in the decline period, compute the linearly declining efficacy
    eff_vec[decline_months] <- efficacy * (1 - (decline_months - valid_months) / (zero_month - valid_months))
  }
  
  # The remaining months after zero_month remain zero (already set by numeric())
  return(eff_vec)
}


#################################################
#################################################
vaccine_efficacy_list <- list(
  
    eff_RSVMA_palivizumab  = eff_RSVMA_palivizumab,
    eff_inpat_palivizumab  = eff_inpat_palivizumab,
    eff_ICU_palivizumab    = eff_ICU_palivizumab,
  
    # Calculate the efficacy of RSVpreF in each month
    eff_RSVMA_RSVpreF  = vaccine_efficacy(efficacy_RSVMA_RSVpreF, valid_months_RSVpreF, zero_month ),
    eff_inpat_RSVpreF  = vaccine_efficacy(efficacy_inpat_RSVpreF, valid_months_RSVpreF, zero_month ),
    eff_ICU_RSVpreF    = vaccine_efficacy(efficacy_ICU_RSVpreF, valid_months_RSVpreF, zero_month ),

    # Calculate the efficacy of Nirsevimab in each month
    eff_RSVMA_nirsevimab  = vaccine_efficacy(efficacy_RSVMA_nirsevimab, valid_months_nirsevimab, zero_month ),
    eff_inpat_nirsevimab  = vaccine_efficacy(efficacy_inpat_nirsevimab, valid_months_nirsevimab, zero_month ),
    eff_ICU_nirsevimab    = vaccine_efficacy(efficacy_ICU_nirsevimab,  valid_months_nirsevimab, zero_month )
)

```


# Sample individual level characteristics

```{r}
##  characteristics 

create_cohort <- function(n_i) {
  # Everyone starts in state "NB" and we sample birth months and term status.
  v_M_init   <- rep("NB", n_i)
  v_monthborn <- sample(1:12, size = n_i, replace = TRUE) # months since start of the simulation
  v_risk     <- sample(names(v_risk_prob), size = n_i, replace = TRUE, prob = v_risk_prob) # Vector for the risk level of each infants 
  v_pvz <- ifelse(v_risk == "HighRisk" & v_monthborn > sim_to_rsv_month_gap, 1, 0) # Vector for getting pvz
  
  # Vaccination month columns (initialized to NA)
  v_RSVpreF_Month      <- rep(NA, n_i)
  v_nirsevimab_Month   <- rep(NA, n_i)
  v_nirsevimab_Month_y2   <- rep(NA, n_i)
  v_palivizumab_Month_y1 <- rep(NA, n_i)
  v_palivizumab_Month_y2 <- rep(NA, n_i)
  
  df_X <- data.frame(
    ID = 1:n_i, 
    MonthBorn = v_monthborn, 
    M_init = v_M_init,
    Risk = v_risk,
    pvz = v_pvz,
    RSVpreF_Month = v_RSVpreF_Month, 
    nirsevimab_Month = v_nirsevimab_Month,
    nirsevimab_Month_y2 = v_nirsevimab_Month_y2,
    palivizumab_Month_y1 = v_palivizumab_Month_y1,
    palivizumab_Month_y2 = v_palivizumab_Month_y2
  )
  return(df_X)
}

#df_X <- create_cohort (n_i) 
#head(df_X)  # print the first rows of the dataframe
```


## Vaccinattion strategies

```{r}
#############################################################
#############################################################
# we assume everyone in early preterm group and coverage_palivizumab percentage of people in CMC group get vaccinated.
Palivizumab <- function(df_X, coverage_palivizumab_y2) {
  
  # Assign vaccination to eligible preterm infants based on coverage probability and condition
  vacc_eligible <- (df_X$pvz ==1)
  
  # Set nirsevimab_Month to their birth month
  df_X$palivizumab_Month_y1[vacc_eligible] <-  df_X$MonthBorn[vacc_eligible]
  
  
  # Assign vaccination to eligible preterm infants based on coverage probability and condition
  vacc_eligible2 <- (!is.na(df_X$palivizumab_Month_y1))  & (runif(nrow(df_X)) <= (coverage_palivizumab_y2))
  # Set palivizumab_Month to 18 for the second season
  df_X$palivizumab_Month_y2[vacc_eligible2] <- 12+(sim_to_rsv_month_gap+1)

  
  return(df_X)
}

#############################################################
#############################################################
Nirsevimab_Replacement <- function(df_X, coverage_palivizumab_y2) {
  
  # Assign vaccination to eligible preterm infants based on coverage probability
  vacc_eligible <- (df_X$pvz ==1)
  # Set nirsevimab_Month to birth month
  df_X$nirsevimab_Month[vacc_eligible] <- df_X$MonthBorn[vacc_eligible]
  
  # Assign vaccination to eligible preterm infants based on coverage probability and condition
  vacc_eligible2 <- (!is.na(df_X$nirsevimab_Month))  & (runif(nrow(df_X)) <= (coverage_palivizumab_y2))
  # Set nirsevimab_Month to 18 for the second season
  df_X$nirsevimab_Month_y2[vacc_eligible2] <- 12+(sim_to_rsv_month_gap+1)

  
  return(df_X)
}

#############################################################
#############################################################
Nirsevimab_HighRisk_WithCatchup <- function(df_X, coverage_nirsevimab_HighRisk) {
  
  df_X <- Nirsevimab_Replacement(df_X, coverage_palivizumab_y2)
  
  # Assign vaccination to eligible preterm infants based on coverage probability
  vacc_eligible <- (df_X$Risk == "HighRisk") & 
                    is.na(df_X$nirsevimab_Month) & 
                    (runif(nrow(df_X)) <= (coverage_nirsevimab_HighRisk))
  
  # Set nirsevimab_Month to first month of RSV season for those born before RSV season, otherwise to their birth month
  df_X$nirsevimab_Month[vacc_eligible] <- ifelse(df_X$MonthBorn[vacc_eligible] <= sim_to_rsv_month_gap, 
                                                 sim_to_rsv_month_gap+1, 
                                                 df_X$MonthBorn[vacc_eligible])
  
  return(df_X)
}

#############################################################
#############################################################
Nirsevimab_ModerateRisk_WithCatchup <- function(df_X, coverage_nirsevimab_ModerateRisk) {
  
  # Assign vaccination to eligible preterm infants based on coverage probability
  vacc_eligible <- (df_X$Risk == "ModerateRisk") &
                    is.na(df_X$RSVpreF_Month) & 
                    (runif(nrow(df_X)) <= (coverage_nirsevimab_ModerateRisk))
  
  # Set nirsevimab_Month to first month of RSV season for those born before RSV season, otherwise to their birth month
  df_X$nirsevimab_Month[vacc_eligible] <- ifelse(df_X$MonthBorn[vacc_eligible] <= sim_to_rsv_month_gap, 
                                                 sim_to_rsv_month_gap+1, 
                                                 df_X$MonthBorn[vacc_eligible])
  
  return(df_X)
}

#############################################################
#############################################################
Nirsevimab_WithCatchup <- function(df_X, coverage_nirsevimab_ModerateRisk) {
  
  # Assign vaccination to eligible preterm infants based on coverage probability
  vacc_eligible <- (df_X$Risk %in% c("ModerateRisk", "LowRisk")) &
                    (runif(nrow(df_X)) <= (coverage_nirsevimab_ModerateRisk))
  
  # Set nirsevimab_Month to first month of RSV season for those born before RSV season, otherwise to their birth month
  df_X$nirsevimab_Month[vacc_eligible] <- ifelse(df_X$MonthBorn[vacc_eligible] <= sim_to_rsv_month_gap, 
                                                sim_to_rsv_month_gap+1, 
                                                df_X$MonthBorn[vacc_eligible])
  
  return(df_X)
}


#############################################################
#############################################################
RSVpreF_RSVSeason <- function(df_X, coverage_RSVpreF) {
  
  
  # Assign vaccination
  vacc_eligible <- (df_X$Risk %in% c("ModerateRisk", "LowRisk")) &
                    (df_X$MonthBorn > sim_to_rsv_month_gap) & 
                    (runif(nrow(df_X)) <= (coverage_RSVpreF))
  
 # Set RSVpreF_Month to their birth month
  df_X$RSVpreF_Month[vacc_eligible] <-  df_X$MonthBorn[vacc_eligible]
  
  return(df_X)
}



#df_X <- create_cohort (n_i)

#df_X <- Palivizumab (df_X, coverage_palivizumab_y2) 
#df_X <- Nirsevimab_Replacement(df_X, coverage_palivizumab_y2)

#table(df_X$nirsevimab_Month)

```


# Define Simulation Functions



## Probability function

The `state_transition` function updates the states of every cycle is shown below.

```{r}
########################################################
########################################################
# Function for calculating the probability of hospotalization
hospitalization_probability <- function(hosp_prob_df,
                                        eff_inpat_palivizumab,
                                        da = 0.25) {
  
  # Manupulate the inputs the same way as estimated
  hosp_prob_df$month_of_life <- hosp_prob_df$month_of_life + da
  hosp_prob_df$risk <- factor(hosp_prob_df$risk, levels = c("LowRisk", "ModerateRisk", "HighRisk"))
  hosp_prob_df$calendar_month <- factor(
    hosp_prob_df$calendar_month,
    levels = c(8, 1:7, 9:12)
  )
  
  # 3. Identify which rows are ãgoodã (no missing predictor data)
  good <- complete.cases(
    hosp_prob_df[, c("month_of_life", "pvz", "risk", "calendar_month")]
  )
  
  # 4. Build the design matrix only for the good rows
  X_good <- model.matrix(
    ~ I(1/month_of_life) + month_of_life + I(month_of_life^2) + I(month_of_life^3) +
      pvz + risk + 
      calendar_month,
    data = hosp_prob_df[good, , drop = FALSE]
  )
  
  # 5. Align your beta vector
  beta_good <- Hosp_model_beta[colnames(X_good)]
  
  # 6. Compute the linear predictor and probabilities for the good rows
  lp_good   <- X_good %*% beta_good
  prob_good <- as.numeric(1 / (1 + exp(-lp_good)))
  
  # 7. Assemble fullãlength prediction vector, defaulting to 0
  pred_prob <- numeric(nrow(hosp_prob_df))  # all zeros
  pred_prob[good] <- prob_good              # fill in the ãgoodã ones
  
  
    # 8. Adjust for palivizumab efficacy where pvz == 1
  #    multiply by 1 / (1 - eff_inpat_palivizumab)
  adj_factor <- 1 / (1 - eff_inpat_palivizumab)
  pred_prob[hosp_prob_df$pvz == 1] <- 
  pred_prob[hosp_prob_df$pvz == 1] * adj_factor
  
  return(pred_prob)
}

#############################################################
#############################################################
state_transition <- function(l_params, M_t,Tr_t, t, df_X) {

  # Define probability of being born in cycle t
  p_NB <- as.numeric(df_X$MonthBorn == t)
  
  
  p_H_D <- l_params$p_mort
  
  p_RSV_D <- ifelse(Tr_t %in% c("ICU", "PW"), l_params$p_mort_Inp, l_params$p_mort)
  
  
  month_of_life   <- ifelse(t >= df_X$MonthBorn, t - df_X$MonthBorn, NA)
  
  calendar_month <- ((t - 1) + (sim_start_month - 1)) %% 12 + 1
  
  hosp_prob_df <- data.frame(
  month_of_life   = month_of_life,
  pvz             = df_X$pvz,
  risk            = df_X$Risk,
  calendar_month  = calendar_month
  )
  
  # Calculate probability of hospitalization using your logistic function
  p_H_Inp <- hospitalization_probability(hosp_prob_df, eff_inpat_palivizumab)
  
  
  # Calculate the probability of getting RSV, based on probability of hospitalization
  p_H_RSV <- ifelse(!is.na(month_of_life), p_H_Inp / prob_RSVMA_Inp[month_of_life+1], 0)
  p_H_RSV <- pmin(p_H_RSV, 1)
  
  # Create matrix of state transition probabilities (rows: states, columns: individuals)
  m_p_t <- matrix(0, nrow = n_states, ncol = n_i)
  rownames(m_p_t) <- v_names_states
  
  # Transitions when in state NB
  idx <- M_t == "NB"
  m_p_t["NB", idx]  <- 1 - p_NB[idx]
  m_p_t["H", idx]   <-     p_NB[idx] * (1 - p_H_RSV[idx])
  m_p_t["RSV", idx] <-     p_NB[idx] *      p_H_RSV[idx]
  m_p_t["D", idx]   <- 0
  
  # Transitions when in state H
  idx <- M_t == "H"
  m_p_t["H", idx]   <- (1 - p_H_D) * (1 - p_H_RSV[idx])
  m_p_t["RSV", idx] <- (1 - p_H_D) *      p_H_RSV[idx]
  m_p_t["D", idx]   <-      p_H_D
  
  # Transitions when in state RSV
  idx <- M_t == "RSV"
  m_p_t["H", idx]  <- (1 - p_RSV_D[idx])
  m_p_t["D", idx]  <-      p_RSV_D[idx]
  
  # Transitions when in state D (absorbing)
  idx <- M_t == "D"
  m_p_t["D", idx] <- 1
  
  # Transpose so that each row corresponds to an individual
  prob_matrix <- t(m_p_t)
  m_t <- samplev(prob_matrix, 1)

  return(m_t)
}

```



## Function for assigning treatment type

```{r}
#############################################################
#############################################################
# Function for calculating probebility mudifier for hospitalization and ICU, based on vaccination
Vaccine_effect_modifier <- function(vaccine_efficacy_list, t, df_X) {
  with(as.list(vaccine_efficacy_list), {
  # Initialize efficacy vectors
  eff_RSVMA <- rep(0, n_i)
  eff_inpat <- rep(0, n_i)
  eff_ICU   <- rep(0, n_i)

  # Define indices for vaccine recipients
  eff_indices_RSVpreF <- !is.na(df_X$RSVpreF_Month) & (df_X$RSVpreF_Month <= t)
  
  eff_indices_nirsevimab <- !is.na(df_X$nirsevimab_Month) & (df_X$nirsevimab_Month <= t)
  eff_indices_nirsevimab_y2 <- !is.na(df_X$nirsevimab_Month_y2) & (df_X$nirsevimab_Month_y2 <= t) & (t < 25)
  
  eff_indices_palivizumab_y1 <- !is.na(df_X$palivizumab_Month_y1) & (df_X$palivizumab_Month_y1 <= t) & (t < 13)
  eff_indices_palivizumab_y2 <- !is.na(df_X$palivizumab_Month_y2) & (df_X$palivizumab_Month_y2 <= t) & (t < 25)

  # Calculate efficacy for palivizumab (RSV season)
  eff_RSVMA[eff_indices_palivizumab_y1] <- pmax(eff_RSVMA[eff_indices_palivizumab_y1], eff_RSVMA_palivizumab)
  eff_inpat[eff_indices_palivizumab_y1] <- pmax(eff_inpat[eff_indices_palivizumab_y1], eff_inpat_palivizumab)
  eff_ICU  [eff_indices_palivizumab_y1] <- pmax(eff_ICU  [eff_indices_palivizumab_y1], eff_ICU_palivizumab)
  
  # Second season
  eff_RSVMA[eff_indices_palivizumab_y2] <- pmax(eff_RSVMA[eff_indices_palivizumab_y2], eff_RSVMA_palivizumab)
  eff_inpat[eff_indices_palivizumab_y2] <- pmax(eff_inpat[eff_indices_palivizumab_y2], eff_inpat_palivizumab)
  eff_ICU[eff_indices_palivizumab_y2]   <- pmax(eff_ICU[eff_indices_palivizumab_y2],   eff_ICU_palivizumab)

  # Calculate efficacy for RSVpreF
  diff_RSVpreF <- 1 + t - df_X$RSVpreF_Month[eff_indices_RSVpreF]
  eff_RSVMA[eff_indices_RSVpreF] <- pmax(eff_RSVMA[eff_indices_RSVpreF], eff_RSVMA_RSVpreF[diff_RSVpreF])
  eff_inpat[eff_indices_RSVpreF] <- pmax(eff_inpat[eff_indices_RSVpreF], eff_inpat_RSVpreF[diff_RSVpreF])
  eff_ICU[eff_indices_RSVpreF]   <- pmax(eff_ICU[eff_indices_RSVpreF],   eff_ICU_RSVpreF[diff_RSVpreF])

  # Calculate efficacy for nirsevimab
  diff_nirsevimab <- 1 + t - df_X$nirsevimab_Month[eff_indices_nirsevimab]
  eff_RSVMA[eff_indices_nirsevimab] <- pmax(eff_RSVMA[eff_indices_nirsevimab], eff_RSVMA_nirsevimab[diff_nirsevimab])
  eff_inpat[eff_indices_nirsevimab] <- pmax(eff_inpat[eff_indices_nirsevimab], eff_inpat_nirsevimab[diff_nirsevimab])
  eff_ICU[eff_indices_nirsevimab]   <- pmax(eff_ICU[eff_indices_nirsevimab],   eff_ICU_nirsevimab[diff_nirsevimab])
  
  
  # Calculate efficacy for nirsevimab, second season
  diff_nirsevimab_y2 <- 1 + t - df_X$nirsevimab_Month_y2[eff_indices_nirsevimab_y2]
  eff_RSVMA[eff_indices_nirsevimab_y2] <- pmax(eff_RSVMA[eff_indices_nirsevimab_y2], eff_RSVMA_nirsevimab[diff_nirsevimab_y2])
  eff_inpat[eff_indices_nirsevimab_y2] <- pmax(eff_inpat[eff_indices_nirsevimab_y2], eff_inpat_nirsevimab[diff_nirsevimab_y2])
  eff_ICU[eff_indices_nirsevimab_y2]   <- pmax(eff_ICU[eff_indices_nirsevimab_y2],   eff_ICU_nirsevimab[diff_nirsevimab_y2])

  # Calculate probability modifiers
  pmf_RSVMA <- (1-eff_RSVMA)
  pmf_inpat <- pmin((1-eff_inpat)/(1-eff_RSVMA), 1)
  pmf_ICU   <-  pmin((1-eff_ICU)/(1-eff_inpat), 1)

  return(list(pmf_RSVMA = pmf_RSVMA, pmf_inpat = pmf_inpat, pmf_ICU = pmf_ICU))
  }
  )
}

#############################################################
#############################################################
#The `treatment_type` function assign the type of treatment needed for infants with RSV at every cycle.
treatment_type <- function(vaccine_efficacy_list, l_params, M_t, t, df_X) {

  # Compute vaccine effect modifiers
  pmf_results <- Vaccine_effect_modifier(vaccine_efficacy_list , t, df_X)
  #pmf_RSVMA <- pmf_results$pmf_RSVMA
  pmf_inpat <- pmf_results$pmf_inpat
  pmf_ICU   <- pmf_results$pmf_ICU
  
  
  # We calculate pmf_RSVMA separately, using l_params, for sensitivity analysis. pmf_RSVMA changes in sensitivity analysis.
  vaccine_efficacy_list$eff_RSVMA_palivizumab<- l_params$eff_RSVMA_palivizumab
  vaccine_efficacy_list$eff_RSVMA_RSVpreF <- l_params$eff_RSVMA_RSVpreF
  vaccine_efficacy_list$eff_RSVMA_nirsevimab <- l_params$eff_RSVMA_nirsevimab
  
  
  pmf_results <- Vaccine_effect_modifier(vaccine_efficacy_list, t, df_X)
  pmf_RSVMA <- pmf_results$pmf_RSVMA
  
  # Compute probabilities for different treatment types
  RSVMA_prob <- pmf_RSVMA
  month_of_life <- ifelse(t >= df_X$MonthBorn, t - df_X$MonthBorn, NA)
  Inp_prob <- ifelse(!is.na(month_of_life), prob_RSVMA_Inp[month_of_life+1], 0)
  
  Inp_prob <- pmin(Inp_prob, 1)
  Inp_prob <- Inp_prob * pmf_inpat
  
  
  
  # Calculating the probability of ICU, conditional on hospotalization
  ICU_prob <- case_when(
    df_X$Risk == "HighRisk"     ~ l_params$Prob_ICU_HighRisk,
    df_X$Risk == "ModerateRisk" ~ l_params$Prob_ICU_ModerateRisk,
    TRUE                        ~ l_params$Prob_ICU_LowRisk
  )
  
  # Apply the second season multiplier if t > 12
  if (t > 12) {
    ICU_prob <- ICU_prob * RR_Prob_ICU_Second_season
  }
  
  # Modify probability, based on vaccine efficiency
  ICU_prob <- ICU_prob * pmf_ICU
  
  
  
  ED_prob <- ifelse(!is.na(month_of_life), prob_Outp_ED[month_of_life+1], 0)
  
  m_p_tr <- matrix(0, nrow = n_treatments, ncol = n_i)
  rownames(m_p_tr) <- v_names_treatments
  
  # For states NB, H, D: only "NT" (no treatment) is possible.
  for (state in c("NB", "H", "D")) {
    idx <- M_t == state
    m_p_tr["NT", idx] <- 1
  }
  
  # For state RSV:
  idx <- M_t == "RSV"
  m_p_tr["NT", idx]  <- 1 - RSVMA_prob[idx]
  m_p_tr["ICU",idx] <-      RSVMA_prob[idx] *      Inp_prob[idx] *      ICU_prob[idx]
  m_p_tr["PW", idx]  <-     RSVMA_prob[idx] *      Inp_prob[idx] * (1 - ICU_prob[idx])
  m_p_tr["ED", idx]  <-     RSVMA_prob[idx] * (1 - Inp_prob[idx]) *     ED_prob[idx]
  m_p_tr["DV", idx]  <-     RSVMA_prob[idx] * (1 - Inp_prob[idx]) * (1 -ED_prob[idx])
  
  prob_matrix <- t(m_p_tr)
  #chosen_idx <- vec_sample(prob_matrix)
  #tr_t <- v_names_treatments[chosen_idx]
  tr_t <- samplev(prob_matrix, 1)
  
  return(tr_t)
}

```



##  Cost and utility function

```{r}
#############################################################
#############################################################
#The `Costs` function estimates the costs at every cycle.
Costs <- function (l_params, Tr_t, t, df_X) {
  with(as.list(l_params), {
  # Arguments:
  # Trt: Treatment 
  # Returns:
  # costs accrued in this cycle
  
  
  # Initialize cost vector for all individuals as 0
  c_inpat <- c_outpat <- rep(0, length(Tr_t))
  
  
  # Calculate ICU costs only if there are individuals in ICU
  if (any(Tr_t == "ICU")) {
    # Create a logical mask for ICU individuals
    ICU_mask <- Tr_t == "ICU"
  
    # Pre-compute the length of stay (LoS_ICU) using vectorized operations
    LoS_ICU <-  case_when(
    df_X$Risk == "HighRisk" ~ LOS_icu_HighRisk,
    df_X$Risk == "ModerateRisk" ~ LOS_icu_ModerateRisk,
    TRUE ~ LOS_icu_LowRisk
    )
  
    # Calculate ICU costs
    c_ICU <- PD_ICU * LoS_ICU
  
    # Assign costs to ICU individuals
    c_inpat[ICU_mask] <- c_ICU[ICU_mask]
  }
  
  
  # Calculate Pediatric Ward (PW) costs only if there are individuals in PW
  if (any(Tr_t == "PW")) {
    # Logical mask for PW individuals
    PW_mask <- Tr_t == "PW"
  
    # Pre-compute the length of stay (LoS_PW) using vectorized operations
    LoS_PW <-  case_when(
      df_X$Risk == "HighRisk"     ~ LOS_hosp_HighRisk,
      df_X$Risk == "ModerateRisk" ~ LOS_hosp_ModerateRisk,
      TRUE                        ~ LOS_hosp_LowRisk
    )
  
    # Calculate PW costs
    c_PW <- PD_PW * LoS_PW
  
    # Assign costs to PW individuals
    c_inpat[PW_mask] <- c_PW[PW_mask]
  }
  
  # Outpatient cost
  c_outpat <- ifelse(Tr_t == "ED", c_ED, ifelse(Tr_t == "DV", c_DV, 0))
  
  
  # Add vaccine cost if individual received it in month t
  
  c_vac_palivizumab_y1 <- ifelse(!is.na(df_X$palivizumab_Month_y1) & df_X$palivizumab_Month_y1 == t, 
                                 c_palivizumab + c_Admin_palivizumab, 0)
  c_vac_palivizumab_y2 <- ifelse(!is.na(df_X$palivizumab_Month_y2) & df_X$palivizumab_Month_y2 == t, 
                                 c_palivizumab + c_Admin_palivizumab, 0)
  
  c_vac_nirsevimab  <- ifelse(!is.na(df_X$nirsevimab_Month) &  df_X$nirsevimab_Month == t,  c_nirsevimab +  c_Admin_vac, 0)
  c_vac_nirsevimab_y2  <- ifelse(!is.na(df_X$nirsevimab_Month_y2) &  df_X$nirsevimab_Month_y2 == t,  c_nirsevimab +  c_Admin_vac, 0)
  
  c_vac_RSVpreF     <- ifelse(!is.na(df_X$RSVpreF_Month) &     df_X$RSVpreF_Month == t,     c_RSVpreF +     c_Admin_vac, 0)
  
  c_vac <- c_vac_RSVpreF + c_vac_nirsevimab + c_vac_nirsevimab_y2+ c_vac_palivizumab_y1 + c_vac_palivizumab_y2
  
  c_t <- c_inpat+ c_outpat + c_vac
  
  return(list(c_t = c_t, c_inpat = c_inpat, c_vac = c_vac))   # return costs accrued this cycle 
  }
  )
}


#Costs (Tr_t, t, df_X, Str = "No Prevention")

#############################################################
#############################################################
# The `Effs` function to update the utilities at every cycle.
Effs <- function (l_params, M_t, Tr_t, df_X) {
  with(as.list(l_params), {
  # Arguments:
  # M_t: health state occupied by individual i at cycle t (character variable)
  # Tr_t: Treatment type for each individual at cycle t
  # df_X: data frame with individual characteristics data

  u_t <- rep(0, length(M_t))
  
  # Assign base utility for Healthy and RSV states
  u_t[M_t %in% c("H", "RSV")] <- u_H * cycle_length
  
  # Subtract disutilities based on treatment
    # Subtract disutilities based on treatment
  u_t[ Tr_t == "ICU"] <- u_t[Tr_t == "ICU"] - (Du_ICU_Infants)
  u_t[ Tr_t == "PW"]  <- u_t[Tr_t == "PW"]  - (Du_PW_Infants)
  u_t[ Tr_t == "ED"] <- u_t[Tr_t == "ED"] - (Du_ED_Infants) 
  u_t[ Tr_t == "DV"] <- u_t[Tr_t == "DV"] - (Du_DV_Infants)
  
  #u_t[ Tr_t == "ICU"] <- u_t[Tr_t == "ICU"] - (Du_ICU_Infants+ Du_ICU_Caregivers)
  #u_t[ Tr_t == "PW"]  <- u_t[Tr_t == "PW"]  - (Du_PW_Infants + Du_PW_Caregivers)
  #u_t[ Tr_t == "ED"] <- u_t[Tr_t == "ED"] - (Du_ED_Infants + Du_ED_Caregivers) 
  #u_t[ Tr_t == "DV"] <- u_t[Tr_t == "DV"] - (Du_DV_Infants + Du_DV_Caregivers)
  
  
  # Ensure utilities do not go below zero
  u_t <- pmax(u_t, 0)
  
  return(u_t)
  }
  )
}
```



## The Microsimulation function

```{r}

MicroSim <- function(l_params, df_X, n_i, Str, seed) {

  set.seed(seed)

  # Apply vaccination strategies according to Str
  if (Str == "Palivizumab") {
    df_X <- Palivizumab (df_X, coverage_palivizumab_y2)
    
  } else if (Str == "Nirsevimab (High)") {
    df_X <- Nirsevimab_HighRisk_WithCatchup(df_X, coverage_nirsevimab_HighRisk)
    
  } else if (Str == "Nirsevimab (High & Mod)") {
    df_X <- Nirsevimab_HighRisk_WithCatchup(df_X, coverage_nirsevimab_HighRisk)
    df_X <- Nirsevimab_ModerateRisk_WithCatchup (df_X, l_params$coverage_nirsevimab_ModerateRisk)
    
  } else if (Str == "RSVpreF") {
    df_X <- RSVpreF_RSVSeason(df_X, l_params$coverage_RSVpreF)
    
  } else if (Str == "RSVpreF + Nirsevimab (High)") {
    df_X <- RSVpreF_RSVSeason(df_X, l_params$coverage_RSVpreF)
    df_X <- Nirsevimab_HighRisk_WithCatchup(df_X, coverage_nirsevimab_HighRisk)
    
  } else if (Str == "RSVpreF + Nirsevimab (High & Mod)") {
    df_X <- RSVpreF_RSVSeason(df_X, l_params$coverage_RSVpreF)
    df_X <- Nirsevimab_HighRisk_WithCatchup(df_X, coverage_nirsevimab_HighRisk)
    df_X <- Nirsevimab_ModerateRisk_WithCatchup (df_X, l_params$coverage_nirsevimab_ModerateRisk)
    
    
  } else if (Str == "Nirsevimab (Universal)") {
    df_X <- Nirsevimab_HighRisk_WithCatchup(df_X, coverage_nirsevimab_HighRisk)
    df_X <- Nirsevimab_WithCatchup(df_X, l_params$coverage_nirsevimab_ModerateRisk)
  }
  
  # Pre-allocate matrices for health states, treatment, costs, and QALYs.
  m_M    <- m_Tr <- m_C <- m_C_vac <- m_C_inpat <- m_E <- matrix(NA, nrow = n_i, ncol = n_cycles + 1,
                                                     dimnames = list(paste("ind", 1:n_i, sep = " "),
                                                                     paste("cycle", 0:n_cycles, sep = " ")))
  m_M[, 1] <- as.character(df_X$M_init)
  m_Tr[, 1] <- treatment_type(vaccine_efficacy_list, l_params, m_M[, 1], 0, df_X)
  
  cost      <- Costs(l_params, m_Tr[, 1], 0, df_X)
  m_C[, 1]  <- cost$c_t
  m_C_vac[, 1] <- cost$c_vac
  m_C_inpat[, 1] <- cost$c_inpat
  m_E[, 1]  <- Effs(l_params, m_M[, 1], m_Tr[, 1], df_X)
  
  total_treatment_counts <- setNames(rep(0, length(v_names_treatments)), v_names_treatments)
  
  set.seed(seed+1)
  # Loop over cycles (vectorized operations inside)
  for (t in 1:n_cycles) {
    m_M[, t + 1] <- state_transition(l_params, m_M[, t], m_Tr[, t], t, df_X)
    m_Tr[, t + 1] <- treatment_type(vaccine_efficacy_list, l_params, m_M[, t + 1], t, df_X)
    
    # Update treatment counts 
    treatment_counts <- table(m_Tr[, t + 1])
    for (treatment in names(treatment_counts)) {
      total_treatment_counts[treatment] <- total_treatment_counts[treatment] + treatment_counts[treatment]
    }
    
    cost <- Costs(l_params, m_Tr[, t + 1], t, df_X)
    m_C[, t + 1] <- cost$c_t
    m_C_vac[, t + 1] <- cost$c_vac
    m_C_inpat[, t + 1] <- cost$c_inpat
    m_E[, t + 1] <- Effs(l_params, m_M[, t + 1], m_Tr[, t + 1], df_X)
  }
  
  tc <- rowSums(m_C)
  tc_vac <- rowSums(m_C_vac)
  tc_inpat <- rowSums(m_C_inpat)
  te <- rowSums(m_E)
  
  v_du_D <- ifelse(m_M[, n_cycles + 1] == "D", u_rs, 0)  # Vector of dis-utility from death
  te <- te - v_du_D                                      # subtract dis-utility of death from utility 
  
  ICU_count <- total_treatment_counts["ICU"]
  PW_count  <- total_treatment_counts["PW"]
  ED_count  <- total_treatment_counts["ED"]
  DV_count  <- total_treatment_counts["DV"]
  
  D_count   <- sum(m_M[, n_cycles + 1] == "D")
  
  results <- list(tc = tc, tc_vac = tc_vac, tc_inpat = tc_inpat, te = te, 
                  ICU_count = ICU_count, PW_count = PW_count, ED_count = ED_count, DV_count = DV_count, D_count = D_count)
  return(results)
}

```

# 06 Run Microsimulation

```{r, eval = TRUE, echo = TRUE, warning = FALSE, message = FALSE, results = FALSE }
# Set the seed once here for reproducibility.
seed <- 100
set.seed(seed)

# Calculate the efficacy of RSVpreF in each month
l_params$eff_RSVMA_RSVpreF  <- vaccine_efficacy(l_params$efficacy_RSVMA_RSVpreF, valid_months_RSVpreF, zero_month )

# Calculate the efficacy of Nirsevimab in each month
l_params$eff_RSVMA_nirsevimab  <- vaccine_efficacy(l_params$efficacy_RSVMA_nirsevimab, valid_months_nirsevimab, zero_month )

v_tot_qaly <- v_tot_cost <- v_ave_qaly <- v_ave_cost <- v_vac_cost <- v_inpat_cost <-
  v_ICU_count <- v_PW_count <- v_ED_count <- v_DV_count <- v_D_count <- 
  vector("numeric", length = n_str)

names(v_tot_qaly) <- names(v_tot_cost) <- names(v_ave_qaly) <- names(v_ave_cost) <- names(v_inpat_cost) <- 
  names(v_vac_cost) <- names(v_ICU_count) <- names(v_PW_count) <- names(v_ED_count) <- 
  names(v_DV_count) <- names(v_D_count) <- v_names_str


# Time the simulation.
cat("Starting simulation...\n")
sim_time <- system.time({
  
n_sim <- l_params$n_sim

for (j in 1:n_sim) {
  if(j %% (n_sim/10) == 0) {
    cat(sprintf("\r%d%% done", round(j/n_sim*100)))
  }
  
  df_X <- create_cohort(n_i)
  
  for (i in 1:n_str) {
    outcomes <- MicroSim(l_params, df_X = df_X, n_i = n_i, Str = v_names_str[i], seed + j*10)

    v_tot_cost[i] <- v_tot_cost[i] + sum(outcomes$tc) / n_sim
    v_vac_cost[i] <- v_vac_cost[i] + sum(outcomes$tc_vac) / n_sim
    v_inpat_cost[i] <- v_inpat_cost[i] + sum(outcomes$tc_inpat) / n_sim
    v_tot_qaly[i] <- v_tot_qaly[i] + sum(outcomes$te) / n_sim
    
    v_ave_qaly[i] <- v_ave_qaly[i] + mean(outcomes$te) / n_sim
    v_ave_cost[i] <- v_ave_cost[i] + mean(outcomes$tc) / n_sim
    
    v_ICU_count[i] <- v_ICU_count[i] + outcomes$ICU_count / n_sim
    v_PW_count[i] <- v_PW_count[i] + outcomes$PW_count / n_sim
    v_ED_count[i] <- v_ED_count[i] + outcomes$ED_count / n_sim
    v_DV_count[i] <- v_DV_count[i] + outcomes$DV_count / n_sim
    
    v_D_count[i]  <- v_D_count[i]  +  outcomes$D_count/ n_sim
  }
}
  
})

cat("\nTotal simulation time:", sim_time["elapsed"], "seconds\n")

```
```{r}
# Combine vectors into a data frame
results_table <- data.frame(
  Strategy = names(v_tot_cost),
  
  Total_Cost = as.numeric(v_tot_cost),
  Vaccine_Cost = as.numeric(v_vac_cost),
  Inpatient_Cost = as.numeric(v_inpat_cost),
  
  ICU_Count = as.numeric(v_ICU_count),
  PW_Count  = as.numeric(v_PW_count),
  ED_Count  = as.numeric(v_ED_count),
  DV_Count  = as.numeric(v_DV_count),
  
  D_Count  = as.numeric(v_D_count),
  
  Total_QALY = as.numeric(v_tot_qaly)
)

#results_table <- results_table %>% 
#  filter(Strategy != "No Prevention")

#Identify the cost & QALY of "Base strategy"
base_case_cost <- results_table$Total_Cost[results_table$Strategy == l_params$base_str]
base_case_qaly <- results_table$Total_QALY[results_table$Strategy == l_params$base_str]

#Compute incremental cost and QALY
results_table$Incremental_Cost <- results_table$Total_Cost - base_case_cost
results_table$Incremental_QALY <- results_table$Total_QALY - base_case_qaly

# 3) Compute ICER (Incremental Cost-Effectiveness Ratio)
#    For "No prevention" itself, this will be 0/0, which yields NaN or Inf,
#    so you can leave it as is or explicitly set it to NA.
results_table$ICER <- results_table$Incremental_Cost / results_table$Incremental_QALY

# Sort the table by Total_Cost
#results_table <- results_table[order(results_table$Total_Cost), ]

# Save the results to a CSV file
output_file <- "RSV_results.csv"
write.csv(results_table, file = output_file, row.names = FALSE)

# Print the file location
cat("Results saved to:", output_file, "\n")


print(results_table)
```



# Visualize results

```{r}
# Standard of care
#plot(density(outcomes_NoVac$tc), main = paste("Total cost per person"),  xlab = "Cost ($)")
#plot(density(outcomes_NoVac$te), main = paste("Total QALYs per person"), xlab = "QALYs")
#plot_trace_microsim(outcomes_NoVac$m_M)  # health state trace
```


# Cost-effectiveness analysis (CEA) 
```{r}
# store the mean costs of each strategy in a new variable C (vector of costs)
#v_C <- c(outcomes_NoVac$tc_hat, outcomes_MonAnt$tc_hat, outcomes_MatVac$tc_hat, outcomes_InfVacL1$tc_hat)
v_C <- v_tot_cost
  
# store the mean QALYs of each strategy in a new variable E (vector of effects)
#v_E <- c(outcomes_NoVac$te_hat, outcomes_MonAnt$te_hat, outcomes_MatVac$te_hat, outcomes_InfVacL1$te_hat)
v_E <- v_tot_qaly

# Strategy names
strategies <- v_names_str

# use dampack to calculate the ICER
df_cea <- calculate_icers(cost       = v_C,
                          effect     = v_E,
                          strategies = strategies)
df_cea
```



```{R}
## CEA table in proper format 
table_cea <- format_table_cea(df_cea) 
table_cea
```


```{r}
## CEA frontier 
ICER_Plot <- plot(df_cea, label = "all", txtsize = 14) +
  expand_limits(x = max(table_cea$QALYs) + 0.1) +
  theme(legend.position = c(0.15, 0.85))

# Save the plot to a file
ggsave(filename = "RSV_ICER_Plot.png", plot = ICER_Plot, width = 8, height = 6, dpi = 300)

# Display the plot in the document
ICER_Plot
```


```{r}
## CEA table in proper format 
table_cea <- format_table_cea(df_cea)
table_cea
```

# Deterministic Sensitivity Analysis (DSA)

```{r}

microsim <- function(l_params, df_X, n_i, Str, seed) {
  set.seed(seed)
  # Apply vaccination strategies according to Str
  if (Str == "Palivizumab") {
    df_X <- Palivizumab (df_X, coverage_palivizumab_y2) 
    
  } else if (Str == "Nirsevimab (High)") {
    df_X <- Nirsevimab_HighRisk_WithCatchup(df_X, coverage_nirsevimab_HighRisk)
    
  } else if (Str == "Nirsevimab (High & Mod)") {
    df_X <- Nirsevimab_HighRisk_WithCatchup(df_X, coverage_nirsevimab_HighRisk)
    df_X <- Nirsevimab_ModerateRisk_WithCatchup (df_X, l_params$coverage_nirsevimab_ModerateRisk)
    
  } else if (Str == "RSVpreF") {
    df_X <- RSVpreF_RSVSeason(df_X, l_params$coverage_RSVpreF)
    
  } else if (Str == "RSVpreF + Nirsevimab (High)") {
    df_X <- RSVpreF_RSVSeason(df_X, l_params$coverage_RSVpreF)
    df_X <- Nirsevimab_HighRisk_WithCatchup(df_X, coverage_nirsevimab_HighRisk)
    
  } else if (Str == "RSVpreF + Nirsevimab (High & Mod)") {
    df_X <- RSVpreF_RSVSeason(df_X, l_params$coverage_RSVpreF)
    df_X <- Nirsevimab_HighRisk_WithCatchup(df_X, coverage_nirsevimab_HighRisk)
    df_X <- Nirsevimab_ModerateRisk_WithCatchup (df_X, l_params$coverage_nirsevimab_ModerateRisk)
    
    
  } else if (Str == "Nirsevimab (Universal)") {
    df_X <- Nirsevimab_HighRisk_WithCatchup(df_X, coverage_nirsevimab_HighRisk)
    df_X <- Nirsevimab_WithCatchup(df_X, l_params$coverage_nirsevimab_ModerateRisk)
  }
  
  # Pre-allocate matrices for health states, treatment, costs, and QALYs.
  m_M    <- m_Tr <- m_C <- m_E <- matrix(NA, nrow = n_i, ncol = n_cycles + 1,
                                                     dimnames = list(paste("ind", 1:n_i, sep = " "),
                                                                     paste("cycle", 0:n_cycles, sep = " ")))
  m_M[, 1] <- as.character(df_X$M_init)
  m_Tr[, 1] <- treatment_type(vaccine_efficacy_list, l_params, m_M[, 1], 0, df_X)
  
  cost      <- Costs(l_params, m_Tr[, 1], 0, df_X)
  m_C[, 1]  <- cost$c_t
  m_E[, 1]  <- Effs(l_params, m_M[, 1], m_Tr[, 1], df_X)
  
  set.seed(seed+1)
  # Loop over cycles (vectorized operations inside)
  for (t in 1:n_cycles) {
    m_M[, t + 1] <- state_transition(l_params, m_M[, t], m_Tr[, t], t, df_X)
    m_Tr[, t + 1] <- treatment_type(vaccine_efficacy_list, l_params, m_M[, t + 1], t, df_X)
    
    cost <- Costs(l_params, m_Tr[, t + 1], t, df_X)
    m_C[, t + 1] <- cost$c_t
    m_E[, t + 1] <- Effs(l_params, m_M[, t + 1], m_Tr[, t + 1], df_X)
  }
  
  tc <- rowSums(m_C)
  te <- rowSums(m_E)
  
  v_du_D <- ifelse(m_M[, n_cycles + 1] == "D", u_rs, 0)  # Vector of dis-utility from death
  te <- te - v_du_D                                      # subtract dis-utility of death from utility 
  
  results <- list(tc = tc, te = te)
  return(results)
}

```


```{r}
calculate_ce_out <- function(l_params, n_wtp = 50000){ # User defined
  with(as.list(l_params), {
    ### Run decision model to get transition dynamics array
    
    seed <- 100
    set.seed(seed)
    
    # Calculate the efficacy of RSVpreF in each month
    l_params$eff_RSVMA_RSVpreF  <- vaccine_efficacy(l_params$efficacy_RSVMA_RSVpreF, valid_months_RSVpreF, zero_month)

    # Calculate the efficacy of Nirsevimab in each month
    l_params$eff_RSVMA_nirsevimab  <- vaccine_efficacy(l_params$efficacy_RSVMA_nirsevimab, valid_months_nirsevimab, zero_month)
    
    v_tot_qaly <- v_tot_cost <- 
    vector("numeric", length = n_str)

    names(v_tot_qaly) <- names(v_tot_cost) <- v_names_str
  

    for (j in 1:n_sim) {
      
      df_X <- create_cohort(n_i)
  
      for (i in 1:n_str) {
        outcomes <- microsim(l_params, df_X = df_X, n_i = n_i, Str = v_names_str[i], seed + j*10)

        v_tot_cost[i] <- v_tot_cost[i] + sum(outcomes$tc) / n_sim
        v_tot_qaly[i] <- v_tot_qaly[i] + sum(outcomes$te) / n_sim
      }
    }
      
    #Identify the cost & QALY of "Base strategy"
    base_str_cost <- v_tot_cost[base_str]
    base_str_qaly <- v_tot_qaly [base_str]
    
    ## Vector with discounted net monetary benefits (NMB)
    v_nmb <- ((v_tot_qaly-base_str_qaly) * n_wtp - (v_tot_cost-base_str_cost))/1000
    #v_nmb <- ((v_tot_qaly) * n_wtp - (v_tot_cost))/1000
    
    ## data.frame with discounted costs, effectiveness and NMB
    df_ce <- data.frame(Strategy = v_names_str,
                        Cost     = v_tot_cost,
                        Effect   = v_tot_qaly,
                        NMB      = v_nmb)
    
    return(df_ce)
  }
  )
}

#calculate_ce_out (l_params)

```


# list of parameters
```{r}

############################################################
############################################################
prm <- list(
  
  base_str = "No Intervention",
  
  n_sim = 10,        # Number of simulation #########################################################################

  PD_ICU = 4615, # Cost per day for ICU, from Vadlamudi 2025
  PD_PW = 2283,  # Cost per day for PW, from Vadlamudi 2025

  c_ED  = 342,            # Cost of ED visit, from Shoukat 2023
  c_DV = 229,            # Cost of doctor visit, from Shoukat 2023

  c_RSVpreF           = 125,        # Price of RSVpreF per dose
  c_nirsevimab         = 450,      # Price of nirsevimab per dose
  c_Admin_vac         = 15,        # cost of admin per dose of vaccine
  
  c_palivizumab       = 3600,  # cost of pvz per season
  c_Admin_palivizumab = 150,       # Cost of admin for pvz
  
  # Disutility for each treatment
  # Disutility for each treatment
  Du_ICU_Infants = 0.0245,
  Du_ICU_Caregivers = 0.0097,
  
  Du_PW_Infants  = 0.0169,
  Du_PW_Caregivers  = 0.0067,
  
  Du_ED_Infants  = 0.0135, 
  Du_ED_Caregivers  = 0.00675,
  
  Du_DV_Infants  = 0.00845,
  Du_DV_Caregivers  = 0.00423,
  
  
  #Probability of ICU, if hosp:
  Prob_ICU_LowRisk = AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_LowRisk", "Mean"],
  Prob_ICU_ModerateRisk = AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_ModerateRisk", "Mean"],
  Prob_ICU_HighRisk = AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_HighRisk", "Mean"],
  
  #Length of stay:
  # Length of stay for hospitalization, without ICU 
  LOS_hosp_LowRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_LowRisk", "Mean"],
  LOS_hosp_ModerateRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_ModerateRisk", "Mean"],
  LOS_hosp_HighRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_HighRisk", "Mean"],


  # Length of stay in ICU
  LOS_icu_LowRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_LowRisk", "Mean"],
  LOS_icu_ModerateRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_ModerateRisk", "Mean"],
  LOS_icu_HighRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_HighRisk", "Mean"],
  
  # vaccine coverage
  coverage_RSVpreF  = 0.65,
  coverage_nirsevimab_ModerateRisk  = 0.7,
  
  # Vaccine eficacy
  # pvz from NACI
  eff_RSVMA_palivizumab = 0.7,
  
  # Efficacy for RSVpreF from Kampmann 2023
  efficacy_RSVMA_RSVpreF  = 0.525,

  # Efficacy for nirsevimab from Simûçes 2023
  efficacy_RSVMA_nirsevimab  = 0.795,
  
  
  p_mort = AllMetrics_list[AllMetrics_list$Variable == "monthly_mortality", "Mean"],
  p_mort_Inp = AllMetrics_list[AllMetrics_list$Variable == "monthly_mortality", "Mean"]
)


# function for simple range
rng <- function(param){
  l <- param - 0.25*param
  u <- param + 0.25*param
  result <- list(l = l, u = u)
  
  return(result)
}


############################################################
############################################################
# lower range of parameters
prm_l <- list(
  PD_ICU = rng(prm$PD_ICU)$l, # Cost per day for ICU, from Vadlamudi 2025
  PD_PW = rng(prm$PD_PW)$l,  # Cost per day for PW, from Vadlamudi 2025

  c_ED  = rng(prm$c_ED)$l,            # Cost of ED visit, from Shoukat 2023
  c_DV = rng(prm$c_DV)$l,            # Cost of doctor visit, from Shoukat 2023

  c_RSVpreF     = 100,        # Price of RSVpreF per dose
  c_nirsevimab  = 400,      # Price of nirsevimab per dose
  c_Admin_vac   = 0,        # cost of admin per dose of vaccine
  
  c_palivizumab       = rng(prm$c_palivizumab)$l,  # cost of pvz per season
  c_Admin_palivizumab = 0,       # Cost of admin for pvz
  
  # Disutility for each treatment
  Du_ICU_Infants = 0.0145,    
  Du_PW_Infants  = 0.01,    
  Du_ED_Infants  = 0.008, # rng(prm$Du_ED_Infants)$l,    
  Du_DV_Infants  = 0.005, #rng(prm$Du_DV_Infants)$l,
  
  #Probability of ICU, if hosp:
  Prob_ICU_LowRisk = AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_LowRisk", "LCL"],
  Prob_ICU_ModerateRisk = AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_ModerateRisk", "LCL"],
  Prob_ICU_HighRisk = AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_HighRisk", "LCL"],
  
  #Length of stay:
  # Length of stay for hospitalization, without ICU 
  LOS_hosp_LowRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_LowRisk", "LCL"],
  LOS_hosp_ModerateRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_ModerateRisk", "LCL"],
  LOS_hosp_HighRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_HighRisk", "LCL"],


  # Length of stay in ICU
  LOS_icu_LowRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_LowRisk", "LCL"],
  LOS_icu_ModerateRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_ModerateRisk", "LCL"],
  LOS_icu_HighRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_HighRisk", "LCL"],
  
  
  # vaccine coverage
  coverage_RSVpreF  = 0.5,
  coverage_nirsevimab_ModerateRisk  = 0.6,
  
  # Vaccine eficacy
  # pvz from NACI
  eff_RSVMA_palivizumab = 0.19,
  
  # Efficacy for RSVpreF
  efficacy_RSVMA_RSVpreF  = 0.287,

  # Efficacy for nirsevimab
  efficacy_RSVMA_nirsevimab  = 0.659,
  
  p_mort_Inp = AllMetrics_list[AllMetrics_list$Variable == "monthly_mortality", "LCL"]
)


############################################################
############################################################
# Upper range of parameters
prm_u <- list(
  PD_ICU = rng(prm$PD_ICU)$u, # Cost per day for ICU, from Vadlamudi 2025
  PD_PW = rng(prm$PD_PW)$u,  # Cost per day for PW, from Vadlamudi 2025

  c_ED = rng(prm$c_ED)$u,            # Cost of ED visit, from Shoukat 2023
  c_DV = rng(prm$c_DV)$u,            # Cost of doctor visit, from Shoukat 2023

  c_RSVpreF     = 250,        # Price of RSVpreF per dose
  c_nirsevimab  = 950,      # Price of nirsevimab per dose
  c_Admin_vac   = 30,        # cost of admin per dose of vaccine
  
  c_palivizumab       = rng(prm$c_palivizumab)$u,  # cost of pvz per season
  c_Admin_palivizumab = rng(prm$c_Admin_palivizumab)$u,       # Cost of admin for pvz
  
  # Disutility for each treatment
  Du_ICU_Infants = 0.1053,    
  Du_PW_Infants  = 0.0726,    
  Du_ED_Infants  = 0.0454, #rng(prm$Du_ED_Infants)$u,    
  Du_DV_Infants  = 0.0454, #rng(prm$Du_DV_Infants)$u,
  
  #Probability of ICU, if hosp:
  Prob_ICU_LowRisk = AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_LowRisk", "UCL"],
  Prob_ICU_ModerateRisk = AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_ModerateRisk", "UCL"],
  Prob_ICU_HighRisk = AllMetrics_list[AllMetrics_list$Variable == "Prob_ICU_HighRisk", "UCL"],
  
  #Length of stay:
  # Length of stay for hospitalization, without ICU 
  LOS_hosp_LowRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_LowRisk", "UCL"],
  LOS_hosp_ModerateRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_ModerateRisk", "UCL"],
  LOS_hosp_HighRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_hosp_HighRisk", "UCL"],


  # Length of stay in ICU
  LOS_icu_LowRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_LowRisk", "UCL"],
  LOS_icu_ModerateRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_ModerateRisk", "UCL"],
  LOS_icu_HighRisk = AllMetrics_list[AllMetrics_list$Variable == "LOS_icu_HighRisk", "UCL"],
  
  # vaccine coverage
  coverage_RSVpreF  = 0.8,
  coverage_nirsevimab_ModerateRisk  = 0.9,
  
  # Vaccine eficacy
  # pvz from NACI
  eff_RSVMA_palivizumab = 0.9,
  
  # Efficacy for RSVpreF
  efficacy_RSVMA_RSVpreF  = 0.689,

  # Efficacy for nirsevimab
  efficacy_RSVMA_nirsevimab  = 0.877,
  
  p_mort_Inp = 0.00192 #Assumption used by NACI
)


```




## One-way sensitivity analysis (OWSA)

```{r}

# Strategies
v_names_str <- c("No Intervention",
                 "Palivizumab",
                 "Nirsevimab (High & Mod)",
                 "RSVpreF",
                 "RSVpreF + Nirsevimab (High)",
                 "RSVpreF + Nirsevimab (High & Mod)",
                 "Nirsevimab (Universal)"
                 )
n_str <- length(v_names_str)


# Try the calculate_ce_out() function
df_ce <- calculate_ce_out(prm, n_wtp = 50000)
df_ce
```

```{r}

options(scipen = 999) # disabling scientific notation in R
# dataframe containing all parameters, their base case values, and the min and 
# max values of the parameters of interest 


df_params_owsa <- data.frame(pars = c("c_RSVpreF", "c_nirsevimab", 
                                      "PD_ICU", "PD_PW", "c_ED", "c_DV", 
                                      #"Du_ICU_Infants", "Du_PW_Infants", "Du_ED_Infants", "Du_DV_Infants",
                                      "coverage_RSVpreF", "coverage_nirsevimab_ModerateRisk",
                                      "eff_RSVMA_palivizumab", "efficacy_RSVMA_RSVpreF", "efficacy_RSVMA_nirsevimab",
                                      #"Prob_ICU_LowRisk","Prob_ICU_ModerateRisk","Prob_ICU_HighRisk",
                                      #"LOS_hosp_LowRisk","LOS_hosp_ModerateRisk", "LOS_hosp_HighRisk", 
                                      #"LOS_icu_LowRisk", "LOS_icu_ModerateRisk", "LOS_icu_HighRisk",
                                      "p_mort_Inp"),
                             
                             min  = c(prm_l$c_RSVpreF, prm_l$c_nirsevimab, 
                                      prm_l$PD_ICU, prm_l$PD_PW, prm_l$c_ED, prm_l$c_DV,
                                      #prm_l$Du_ICU_Infants, prm_l$Du_PW_Infants, prm_l$Du_ED_Infants, prm_l$Du_DV_Infants,
                                      prm_l$coverage_RSVpreF, prm_l$coverage_nirsevimab_ModerateRisk,
                                      prm_l$eff_RSVMA_palivizumab, prm_l$efficacy_RSVMA_RSVpreF, prm_l$efficacy_RSVMA_nirsevimab,
                                      #prm_l$Prob_ICU_LowRisk, prm_l$Prob_ICU_ModerateRisk, prm_l$Prob_ICU_HighRisk,
                                      #prm_l$LOS_hosp_LowRisk, prm_l$LOS_hosp_ModerateRisk, prm_l$LOS_hosp_HighRisk, 
                                      #prm_l$LOS_icu_LowRisk, prm_l$LOS_icu_ModerateRisk, prm_l$LOS_icu_HighRisk,
                                      prm_l$p_mort_Inp),  # min parameter values
                             
                             max  = c(prm_u$c_RSVpreF, prm_u$c_nirsevimab, 
                                      prm_u$PD_ICU, prm_u$PD_PW, prm_u$c_ED, prm_u$c_DV,
                                      #prm_u$Du_ICU_Infants, prm_u$Du_PW_Infants, prm_u$Du_ED_Infants, prm_u$Du_DV_Infants,
                                      prm_u$coverage_RSVpreF, prm_u$coverage_nirsevimab_ModerateRisk,
                                      prm_u$eff_RSVMA_palivizumab, prm_u$efficacy_RSVMA_RSVpreF, prm_u$efficacy_RSVMA_nirsevimab,
                                      #prm_u$Prob_ICU_LowRisk,prm_u$Prob_ICU_ModerateRisk, prm_u$Prob_ICU_HighRisk,
                                      #prm_u$LOS_hosp_LowRisk, prm_u$LOS_hosp_ModerateRisk, prm_u$LOS_hosp_HighRisk, 
                                      #prm_u$LOS_icu_LowRisk, prm_u$LOS_icu_ModerateRisk, prm_u$LOS_icu_HighRisk,
                                      prm_u$p_mort_Inp)  # max parameter values
                             )
owsa_nmb  <- run_owsa_det(params_range     = df_params_owsa,    # dataframe with parameters for OWSA
                          params_basecase  = prm,      # list with all parameters
                          nsamp            = 20,               # number of parameter values ######################################
                          FUN              = calculate_ce_out,  # function to compute outputs
                          outcomes         = c("NMB"),          # output to do the OWSA on
                          strategies       = v_names_str,       # names of the strategies
                          n_wtp            = 50000)              # Willingness to pay
```

```{r}
nice_names_param <- c(
  c_ED                              = "ED cost",
  c_DV                              = "DV cost",
  c_nirsevimab                      = "Nirsevimab price",
  c_RSVpreF                         = "RSVpreF price",
  coverage_RSVpreF                  = "RSVpreF cov.",
  coverage_nirsevimab_ModerateRisk  = "Nirsevimab cov. (mod)",
  eff_RSVMA_palivizumab             = "Palivizumab eff.",
  efficacy_RSVMA_nirsevimab         = "Nirsevimab eff.",
  efficacy_RSVMA_RSVpreF            = "RSVpreF eff.",
  p_mort_Inp                        = "Inpatient Mortality",
  PD_ICU                            = "ICU Cost per Day",
  PD_PW                             = "Ward Cost per Day"
)

owsa_nmb_nice <- owsa_nmb %>%
  mutate(
    parameter = factor(parameter,
                       levels = names(nice_names_param),
                       labels = nice_names_param
    )
  )


nice_names_strats <- c(
  `No.Intervention`                   = "No Intervention",
  `Palivizumab`                       = "Palivizumab",
  `Nirsevimab..High...Mod.`           = "Nirsevimab (High & Mod)",
  `RSVpreF`                           = "RSVpreF",
  `RSVpreF...Nirsevimab..High.`       = "RSVpreF + Nirsevimab (High)",
  `RSVpreF...Nirsevimab..High...Mod.` = "RSVpreF + Nirsevimab (High & Mod)",
  `Nirsevimab..Universal.`            = "Nirsevimab (Universal)"
)

owsa_nmb_nice <- owsa_nmb_nice %>%
  mutate(
    strategy = factor(strategy,
                      levels = names(nice_names_strats),
                      labels = nice_names_strats
    )
  )

```


### Tornado plot, it choose the strategy with highest NMB by defult

```{r}
plot_owsa_tornado <- owsa_tornado(owsa = owsa_nmb_nice)

# Save the plot to a file
ggsave(filename = "owsa_tornado.png", plot = plot_owsa_tornado, width = 8, height = 6, dpi = 300)

plot_owsa_tornado
```




```{r}
plot_owsa <- plot(owsa_nmb_nice, txtsize = 11, n_x_ticks = 5, 
     facet_scales = "free") +
     labs(y = "E[NMB]", x = "Parameter Values") +
     theme(
         legend.text = element_text(size = 11),
         axis.text.x = element_text(size = 7)  # Change this number as needed
     )

ggsave(filename = "owsa(with all-infant).png", plot = plot_owsa, width = 12, height = 8, dpi = 500)

plot_owsa
```

```{r}
plot_owsa <- owsa_nmb_nice %>%
  filter(strategy != "Nirsevimab (Universal)") %>%  # Exclude
  droplevels() %>%
  plot(txtsize = 11, n_x_ticks = 5, facet_scales = "free") +
  labs(y = "E[NMB]", x = "Parameter Values") +
  theme(
    legend.text = element_text(size = 11),
    axis.text.x = element_text(size = 7)
  )

ggsave(filename = "owsa (without all-infant).png", plot = plot_owsa, width = 12, height = 8, dpi = 500)

plot_owsa
```





### Optimal strategy with OWSA

```{r}
#owsa_opt_strat(owsa = owsa_nmb, txtsize = 10)
```



## Two-way sensitivity analysis (TWSA)

```{r}

n_i            <- 20000      # number of births per year ###############################################################

# Strategies
v_names_str <- c("No Intervention",
                 "Palivizumab",
                 "Nirsevimab (High & Mod)",
                 "RSVpreF",
                 "RSVpreF + Nirsevimab (High)",
                 "RSVpreF + Nirsevimab (High & Mod)",
                 "Nirsevimab (Universal)"
                 )
n_str <- length(v_names_str)


# Try the calculate_ce_out() function
df_ce <- calculate_ce_out(prm, n_wtp = 50000)
df_ce
```



```{r}
# dataframe containing all parameters, their basecase values, and the min and 
# max values of the parameters of interest

df_params_twsa <- data.frame(pars = c("c_RSVpreF", "c_nirsevimab"),
                             min  = c(0 , 0),  # min parameter values
                             max  = c(300, 1000)  # max parameter values
                             )

twsa_nmb <- run_twsa_det(params_range    = df_params_twsa,    # dataframe with parameters for TWSA
                         params_basecase = prm,      # list with all parameters
                         nsamp           = 20,                # number of parameter values ####################################
                         FUN             = calculate_ce_out,  # function to compute outputs
                         outcomes        = "NMB",             # output to do the TWSA on
                         strategies      = v_names_str,       # names of the strategies
                         n_wtp           = 50000)              # extra argument to pass to FUN
```
```{r}
nice_names_strats_twsa <- c(
  `No.Intervention`                   = "No Intervention",
  `Palivizumab`                       = "Palivizumab",
  `Nirsevimab..High...Mod.`           = "Nirsevimab (High & Mod)",
  `RSVpreF`                           = "RSVpreF",
  `RSVpreF...Nirsevimab..High.`       = "RSVpreF + Nirsevimab (High)",
  `RSVpreF...Nirsevimab..High...Mod.` = "RSVpreF + Nirsevimab (High & Mod)",
  `Nirsevimab..Universal.`            = "Nirsevimab (Universal)"
)

twsa_nmb_nice <- twsa_nmb %>%
  mutate(
    strategy = factor(strategy,
                      levels = names(nice_names_strats_twsa),
                      labels = nice_names_strats_twsa
    )
  )


twsa_nmb_nice <- twsa_nmb_nice %>% 
  rename(
    `RSVpreF price`      = c_RSVpreF,
    `Nirsevimab price`   = c_nirsevimab
  )

```

### Plot TWSA


```{r}
plot_twsa_nmb <- plot(twsa_nmb_nice, txtsize = 12, facet_scales = "free") +
  scale_fill_manual(
    values = c(
      "No Intervention" = "#999999",                 # neutral gray
      "Palivizumab" = "#000000",                     # black
      "RSVpreF" = "#0072B2",                         # deep blue
      "Nirsevimab (High & Mod)" = "#E69F00",         # orange
      "RSVpreF + Nirsevimab (High)" = "#56B4E9",     # light blue
      "RSVpreF + Nirsevimab (High & Mod)" = "#009E73",# green
      "Nirsevimab (Universal)" = "#F0E442"           # yellow
    )
  ) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) +  # Increase y-axis ticks
  theme(legend.text = element_text(size = 10))

# Save the plot to a file
ggsave(filename = "twsa_nmb.png", plot = plot_twsa_nmb, width = 8, height = 6, dpi = 500)

plot_twsa_nmb
```



